ScPy -- A SuperCollider extension for performing numerical computation via embedded Python

### 2016-08-16 doc/paper.tex
abstract

\maketitle
\tableofcontents

\begin{abstract}
    this is abstract
\end{abstract}

@@

\section{Bibilography}

>>>>

\maketitle

\begin{abstract}
    SuperCollider, a language for live coding and algorithmic synthesis of audio,
    includes features for performing spectral analysis and manipulation of audio streams using the
    Short-Time Fourier Transform (STFT). However, available spectral operations are limited to those
    implemented individually as Unit Generators (UGens). Many basic operations exist and can be
    composed to produce complex effects, however this process is tedious and leaves many of the
    possible effects impossible to create. We present ScPy, a UGen which embeds Python scripts within
    SuperCollider to extend the space of possible effects using the optimized vector operations
    provided by the NumPy and SciPy libraries.
\end{abstract}

@@

\section{Bibliography}
